\textmd{\hmwkClass:\ \hmwkTitle}\\ \small{Due\ on\ \hmwkDueDate}

### 2017-05-18 paper/main.tex
punctuation

Our project aims to explore this view by implementing a simple physics engine
in scheme. We designed the physics engine to be generic and extensible. For
example, it is very straightforward to define new worlds on the underlying
substrate as well as to define new objects and forces within a given world.
This paper presents the design of the infrastructure for the physics engine,
describes how objects and forces can be easily defined and added on top of the
infrastucture, and illustrate several demonstrations of the system on worlds
with gravitational and electrostatic forces

>>>>

Our project aims to explore this view by implementing a simple physics engine
in scheme. We designed the physics engine to be generic and extensible. For
example, it is very straightforward to define new worlds on the underlying
substrate as well as to define new objects and forces within a given world.
This paper presents the design of the infrastructure for the physics engine,
describes how objects and forces can be easily defined and added on top of the
infrastucture, and illustrate several demonstrations of the system on worlds
with gravitational and electrostatic forces.
